Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2022-06-17 thirdPaper/draft/typeConeAssociahedra.tex
Added reference in section 3

In~\cite{Auslander1984}, M.~Auslander showed that the relations in the Grothendieck group of an Artin algebra are generated by the ones given by almost-split sequences precisely when the algebra is of finite representation type.  This result was generalized to $\Hom{}$-finite, Krull-Schmidt exact categories with enough projectives by H.~Enomoto in~\cite{Enomoto}, and to $\Hom{}$-finite, Krull--Schmidt triangulated categories with a cogenerator by J.~Haugland in~\cite{Haugland}. Inspired by these results, we will show in this Section that a similar statement holds (see \cref{thm:relations-g-vecteurs}) for the~$\b{g}$-vectors (or indices) of objects in a~$2$-Calabi--Yau triangulated category.  We will further generalize these results in Section~\ref{sec:extricats} to the setting of Ext-finite, Krull-Schmidt, extriangulated categories with Auslander--Reiten--Serre duality admitting projective objects with certain properties.

>>>>

In~\cite{Butler} and~\cite{Auslander1984}, M.~Butler and M.~Auslander showed that the relations in the Grothendieck group of an Artin algebra are generated by the ones given by almost-split sequences precisely when the algebra is of finite representation type.  This result was generalized to triangulated categories with certain finiteness conditions by J.~Xiao and B.~Zhu in \cite{XiaoZhu}, to~$\Hom{}$-finite, Krull-Schmidt exact categories with enough projectives by H.~Enomoto in~\cite{Enomoto}, to $(n+2)$-angulated categories by F.~Fedele in~\cite{Fedele}, and to $\Hom{}$-finite, Krull--Schmidt triangulated categories with a cogenerator by J.~Haugland in~\cite{Haugland}. Relations in the Grothendieck group of cluster categories have also been studied in~\cite{Palu-grothendieckGroup}.  Inspired by these results, we will show in this Section that a similar statement holds (see \cref{thm:relations-g-vecteurs}) for the~$\b{g}$-vectors (or indices) of objects in a~$2$-Calabi--Yau triangulated category.  We will further generalize these results in Section~\ref{sec:extricats} to the setting of Ext-finite, Krull-Schmidt, extriangulated categories with Auslander--Reiten--Serre duality admitting projective objects with certain properties.
